### 2018-02-10 manuscript.Rnw
random updates

\begin{figure}[!h]
	%\includegraphics[width=1\textwidth]{fig/fig-2.pdf}
	\caption{{\bf \texttt{behavr} table.}
	A: Illustration of a \texttt{behavr} object, core data structure in \texttt{rethomics}.
		The metadata holds a single row for each of the $n$ individuals. 
		Its columns, the $p$ metavariables, are of two kind: either required and defined by the acquisition platform (\emph{i.e.} used to fetch the data) or user-defined (\emph{i.e.} arbitrary).
		In the data, each row is a ``read'' (\emph{i.e.} information about one individual at one time point).
		It is formed of $q$ variables and is expected to have a very large number of reads $k$ for each individual $i$.
		Data and metadata are implicitly joined with the \texttt{id} field.
		Names used for variables and metavariable are only plausible examples that will likely differ in practice. 
		B: Non exhaustive list of use of a \texttt{behavr} table, refered as \texttt{dt}. 
		In addition of operations on data inherited from \texttt{data.table}, we provide utilities designed specifically to act on both            metadata and data.  
	}
	\label{fig:fig-2}
\end{figure}

>>>>

\begin{figure}[!h]
	%\includegraphics[width=1\textwidth]{fig/fig-2.pdf}
	\caption{{\bf \texttt{behavr} table.}
	A: Illustration of a \texttt{behavr} object, core data structure in \texttt{rethomics}.
		The metadata holds a single row for each of the $n$ individuals. 
		Its columns, the $p$ metavariables, are of two kind: either required and defined by the acquisition platform (\emph{i.e.} used to fetch the data) or user-defined (\emph{i.e.} arbitrary).
		In the data, each row is a ``read'' (\emph{i.e.} information about one individual at one time point).
		It is formed of $q$ variables and is expected to have a very large number of reads $k$ for each individual $i$.
		Data and metadata are implicitly joined with the \texttt{id} field.
		Names used for variables and metavariable are only plausible examples that will likely differ in practice. 
		B: Non exhaustive list of uses of a \texttt{behavr} table, refered as \texttt{dt}. 
		In addition to operations on data, which are inherited from \texttt{data.table},
		we provide utilities designed specifically to act on both metadata and data.  
	}
	\label{fig:fig-2}
\end{figure}

### 2018-02-10 manuscript.tex
fixes #6, fixes #3
random updates

\begin{figure}[!h]
	%\includegraphics[width=1\textwidth]{fig/fig-4.pdf}
	\caption{{\bf Visualisation of the periodicity in activity of eight representative animals.}
		A: Double plotted actograms showing activity over the experiment. Transition to LL happens at day 0.
		B: $\chi{}^2$ periodograms over the LL part of the experiment matching the animals in A.
		Titles on top of each facet refer to the label allocated to each individual.
		A version of this figure with all animals is available \nameref{S1-Fig}.
	}
	\label{fig:fig-4}
\end{figure}

@@

\texttt{R} provide one of the richest statistical toolbox available, which allows users to go deeper in he analysis of the extracted variables.
One could, for instance, perform a $\chi{}^2$ test on the number of rhythmic vs arhythmic flies in both genotypes.
To address the same question, we fit a binomial generalised linear model, which shows a strong positive effect of ($p$-value $< 10^{-5}$):
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fit} \hlkwb{<-} \hlkwd{glm}\hlstd{(is_rhythmic} \hlopt{~} \hlstd{genotype, summary_dt,} \hlkwc{family}\hlstd{=}\hlstr{"binomial"}\hlstd{)}

>>>>

\begin{figure}[!h]
	%\includegraphics[width=1\textwidth]{fig/fig-4.pdf}
	\caption{{\bf Visualisation of the periodicity in activity of eight representative animals.}
		A: Double plotted actograms showing activity over the experiment. Transition to LL happens at day 0.
		B: $\chi{}^2$ periodograms over the LL part of the experiment matching the animals in A.
		The blue annotation represents the first peak (if present) above the significance threshold (red line).
		Titles on top of each facet refer to the label allocated to each individual.
		A version of this figure with all animals is available \nameref{S1-Fig}.
	}
	\label{fig:fig-4}
\end{figure}

@@

\texttt{R} provides one of the richest statistical toolbox available, which allows users to go deeper in he analysis of the extracted variables.
One could, for instance, perform a $\chi{}^2$ test on the number of rhythmic vs arhythmic flies in both genotypes.
To address the same question, we fit a binomial generalised linear model, which shows a strong positive effect of genotype Tim/NKCCOX on the probability of being rhythmic ($p$-value $< 10^{-5}$):
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fit} \hlkwb{<-} \hlkwd{glm}\hlstd{(is_rhythmic} \hlopt{~} \hlstd{genotype, summary_dt,} \hlkwc{family}\hlstd{=}\hlstr{"binomial"}\hlstd{)}

### 2018-02-10 results.Rnw
random updates

<<cache=TRUE, warning=FALSE>>=
# we also show a subset of this figure in supplementary materials
figS1A <- ggetho(dt, aes(z = moving), multiplot = 2) +
            # bars n the z axis could 
            #  one could also use stat_tile_etho
            stat_bar_tile_etho() + 
            # divide plot by individual
            facet_wrap( ~ label, ncol = 4) +
            # rename the y axis
            scale_y_discrete(name="Day")
@

<<cache=TRUE, echo=FALSE>>=
#fig_4_picked_labels = paste(c(5,10,33,39, 13,17,22,51), rep(c("NKCCOX/+", "Tim/NKCCOX"), each=4), sep=".")
helper_dt_picked_labs <- data.table(num = c(5,10,33,39, 13,17,22,51),
                                    genotype =  rep(c("NKCCOX/+", "Tim/NKCCOX"), each=4))
helper_dt_picked_labs[,label := interaction(num, genotype)]

@@

\texttt{R} provide one of the richest statistical toolbox available, which allows users to go deeper in he analysis of the extracted variables.
One could, for instance, perform a $\chi{}^2$ test on the number of rhythmic vs arhythmic flies in both genotypes.
To address the same question, we fit a binomial generalised linear model, which shows a strong positive effect of ($p$-value $< 10^{-5}$):
<<>>=
fit <- glm(is_rhythmic ~ genotype, summary_dt, family="binomial")

>>>>

<<cache=TRUE, warning=FALSE, result="hide", message=FALSE>>=
# we also show a subset of this figure in supplementary materials
figS1A <- ggetho(dt, aes(z = moving), multiplot = 2) +
            # bars n the z axis could 
            #  one could also use stat_tile_etho
            stat_bar_tile_etho() + 
            # divide plot by individual
            facet_wrap( ~ label, ncol = 4) +
            # rename the y axis
            scale_y_discrete(name="Day")
@

<<cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE, result="hide">>=
#fig_4_picked_labels = paste(c(5,10,33,39, 13,17,22,51), rep(c("NKCCOX/+", "Tim/NKCCOX"), each=4), sep=".")
helper_dt_picked_labs <- data.table(num = c(5,10,33,39, 13,17,22,51),
                                    genotype =  rep(c("NKCCOX/+", "Tim/NKCCOX"), each=4))
helper_dt_picked_labs[,label := interaction(num, genotype)]

@@

\texttt{R} provides one of the richest statistical toolbox available, which allows users to go deeper in he analysis of the extracted variables.
One could, for instance, perform a $\chi{}^2$ test on the number of rhythmic vs arhythmic flies in both genotypes.
To address the same question, we fit a binomial generalised linear model, which shows a strong positive effect of genotype Tim/NKCCOX on the probability of being rhythmic ($p$-value $< 10^{-5}$):
<<>>=
fit <- glm(is_rhythmic ~ genotype, summary_dt, family="binomial")
